R for Clinical Study Reports and Submission

### 2023-01-13 tlf-assemble.Rmd
Polish text for TLF assemble chapter

1. Combine RTF source code in individual files into one large RTF file. 
1. Leverage Microsoft Word `Toggle Fields` feature to embed RTF files using 
hyperlinks.

@@

> The code below requires r2rtf version >= 0.4.0.

The `r2rtf::assemble_rtf()` function allows user to combine RTF 
source code in individual files into one larger RTF file.

::: {.rmdnote data-latex=""}
One limitation of combining RTF source code is that 
we are not able to specify page orientation of each TLF 
in the combined document. 
:::

@@

Microsoft Words uses toggle fields to embed files into one Word document. 
The approach is a dynamic link between files by providing the absolute file path.

::: {.rmdnote data-latex=""}
There is a slight learning curve on how toggle fields work 
in Microsoft Words. 
After you become familiar with the workflow, 
toggle fields can extend your capability to manage a large amount of TLFs
in RTF format.
:::

The `assemble_docx()` function 
allows you to create a word file with toggle fields as below.
One benefit is to control the page direction of each TLF as below.

@@

By using `Alt + F9` to display the fields and you will 
see information similar to the screenshot below.

@@

If it works, you can see a table similar to the snapshot below
by using `Alt + F9`. 
It is a shortcut to change between results and field display mode.

@@

Now you can update all toggle fields to display all TLFs by 
selecting all fields (`Ctrl + A`), then type `F9`. 
We suggest testing one toggle field before updating all of them.

As the `docx` file contain dynamic links, 
you can keep updating the TLFs if you need to refresh content in 
individual RTF files by selecting all fields (`Ctrl + A`), then type `F9`.

::: {.rmdnote data-latex=""}
If you modify table content in the combined `.docx` file, 
you may get a weird table layout if you update all fields within a toggle field. 
To resolve the issue, please remove all `\* MERGEFORMAT` in the filed mode using `Alt + F9` before updating all toggle fields.
:::

After the combined TLF is ready for delivery, 
you can also unlink toggle fields to save table contents, 
because the absolute path may not work for others.  
To unlink toggle fields, you can select all fields (`Ctrl + A`), 
then type `Ctrl + Shift + F9`.

>>>>

1. Combine RTF source code in individual files into one large RTF file.
1. Leverage the `Toggle Fields` feature in Microsoft Word to embed RTF files using
hyperlinks.

@@

::: {.rmdnote data-latex=""}
The code below requires r2rtf version >= 1.0.0.
:::

The `r2rtf::assemble_rtf()` function allows the user to combine RTF
source code in individual files into one larger RTF file.

::: {.rmdnote data-latex=""}
One limitation of combining RTF source code is that
we are not able to specify the page orientation of each TLF
in the combined document.
:::

@@

Microsoft Word uses toggle fields to embed files into one Word document.
The approach is a dynamic link between files by providing the absolute file path.

::: {.rmdnote data-latex=""}
There is a slight learning curve on how toggle fields work
in Microsoft Word.
After you become familiar with the workflow,
toggle fields can extend your capability to manage a large number of TLFs
in RTF format.
:::

The `assemble_docx()` function
allows you to create a `.docx` file with toggle fields as below.
One benefit is to control the page direction of each TLF as below.

@@

By using Alt + F9 to display the fields and you will
see information similar to the screenshot below.

@@

If it works, you can see a table similar to the snapshot below
by using Alt + F9.
It is a shortcut to change between results and field display mode.

@@

Now you can update all toggle fields to display all TLFs by
selecting all fields (Ctrl + A), then press F9.
We suggest testing one toggle field before updating all of them.

As the `.docx` file contain dynamic links,
you can keep updating the TLFs if you need to refresh content in
individual RTF files by selecting all fields (Ctrl + A), then press F9.

::: {.rmdnote data-latex=""}
If you modify table content in the combined `.docx` file,
you may get a weird table layout if you update all fields within a toggle field.
To resolve the issue, please remove all `\* MERGEFORMAT` in the filed mode using Alt + F9 before updating all toggle fields.
:::

After the combined TLF is ready for delivery,
you can also unlink toggle fields to save table contents,
because the absolute path may only work for some.
To unlink toggle fields, you can select all fields (Ctrl + A),
then press Ctrl + Shift + F9.
